# Collect network data and API requests

## Several useful websites

- [Papers, reviews, dataset, software (tutorial)](https://github.com/briatte/awesome-network-analysis) 
- [Katherine's webpage](http://kateto.net/2016/05/network-datasets/)
- [Kaggle](https://www.kaggle.com/datasets)
- [dataworld](https://data.world/search?q=network+dataset)


## Web scraping

- Web APIs (application programming interface): website offers a set of structured http requests that return JSON or XML files.
- R packages: `rtweet` (twitter), `Rfacebook` (facebook), `RedditExtractoR` (reddit), `imdbapi` (IMDB), `omdbapi`(The Open Movie Database).
  - Using `rtweet` to make API requests
  - Construct Retweet networks
  - Construct Friendship networks
- API request from R. `rjson` (map JSON file to datafram),`rvest` (web scrapping).

## Preparation

```{r,echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(igraph)
library(purrr)
library("stringr")
```

## Twitter API request

### R package `rtweet`

Official website: <https://rtweet.info/index.html>

**Explore the official websites to find more info.**

- All the functions
- Tutorial
- FAQ (possible issues)

Good documentation; Recommended over another R package `twitteR`.

### Preparation

```{r, echo=TRUE, message=FALSE, warning=FALSE}
#install.packages("rtweet")
library("rtweet")
```

### API authorization

Follow <https://rtweet.info/articles/auth.html>

- Create a Twitter App

- Authorization via access token:  `create_token()` automatically saves your token as an environment variable, you’ll be set for future sessions as well!

```{r,echo=TRUE, eval=FALSE}
#save your token as an environment variable for you
create_token(
  app = "your_research_app",
  consumer_key = "consumer_API_key",
  consumer_secret = "consumer_API_secret_key",
  access_token = "access_token",
  access_secret = "access_token_secret")
```

### `rtweet`

**API request**

- [Tweeter Developer](https://developer.twitter.com/en/docs/tweets/search/api-reference/get-search-tweets)
- Send a request specifying parameters; Get response in JSON format
- `search_tweets`: **sampling** from tweets in past 7 days matching keywords (**specified # of tweets**)  -- recent/popular/mixed
- `stream_tweets`: sampling/keyword-filter/user-track/geo-location **live stream** for future time period;(**specified time period**) 

#### `search_tweets`

- limiting searches to 10 keywords and operators
- only past 6-9 days of Tweets


**Parameters:**

- `help()` or see <https://developer.twitter.com/en/docs/tweets/search/api-reference/get-search-tweets>
- `q`: Query to be searched. 
  - Spaces/AND -- both ("data science";"data AND science"); 
  - OR -- either or (data OR science); 
  - '""' -- exact ('"data science"'; "\"data science\""); 
  - "\#datascience" -- track hashtag; 
  - "\@duke" -- track at. 
  - [More about operators](https://developer.twitter.com/en/docs/tweets/rules-and-filtering/overview/standard-operators.html)
- `n`: total number of desired tweets. 
  - At most 18,000 in a single call; 
  - For $>$ 18,000, `retryonratelimit`=TRUE
- `type`: "recent","popular","mixed"
- `include_rts`: whether to include retweets
- `geocode`:  "latitude,longitude,radius" 
- `lang`: language
- `parse`: TRUE(dateframe); FALSE(list)

```{r,echo=TRUE,cache=TRUE}
rt <- search_tweets(
  q="#dukebasketball", #Query to be searched
  n = 10,
include_rts=FALSE,
result_type="recent",
geocode = "36.00,-78.94,5mi"
)
rt

rt <- search_tweets(
  "trump OR president", n = 10,
  lang = "en"
)
rt

search_tweets(
  q="#dukebasketball", #Query to be searched
  n = 10,
include_rts=FALSE,
result_type="recent",
geocode = "36.00,-78.94,5mi"
)
```


---

- dataframe: each row a tweet
- `users_data`: only extract user-related column
- `ts_plot`
- `lat_lng`


```{r,echo=TRUE,cache=TRUE}
## search for 18000 tweets using the rstats hashtag
rt <- search_tweets(
  "#dukebasketball", n = 50000, include_rts = FALSE,
  geocode = "36.00,-78.94,2000mi"
)
rt_dmbb=rt
class(rt)

## preview tweets data
names(rt)


## preview users data
users_data(rt)%>%names()

## plot time series (if ggplot2 is installed)
ts_plot(rt) #Duke vs No. 16 Louisville
```

#### `search_tweets2`

Search different queries independently. 

Other parameters are the same.

```{r,echo=TRUE,cache=TRUE}
st2 <- search_tweets2(
  c("\"data science\"", "rstats OR python"),
  n = 50
)
st2$query
names(st2)
```

#### Visualization

`research_tweets` returns a dataframe. Visualization based on the dataframe.

- `ts_plot`: Creates a ggplot2 plot of the frequency of tweets over a specified interval of time. Using `ggplot2`; 
- Map: Using `lat_lng`

```{r,echo=TRUE,cache=TRUE}
## plot time series of tweets
ts_plot(rt_dmbb, "3 hours") + # a ggplot object
  ggplot2::theme_minimal() + # Add multiple layers directly
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #dukebasketball Twitter statuses from past 6-9 days",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
# an example using `groupby` with ggplot2
ts_plot(rt_dmbb%>%dplyr::group_by(is_quote), "3 hours") + # a ggplot object
  ggplot2::theme_minimal()
```

```{r,echo=TRUE,cache=TRUE}
#install.packages("maps")
## create lat/lng variables using all available tweet and profile geo-location data
rt_dmbbll <- lat_lng(rt_dmbb)
names(rt_dmbbll)[!names(rt_dmbbll)%in%names(rt_dmbb)]

## plot state boundaries
par(mar = c(0, 0, 0, 0))
maps::map("state","north carolina", lwd = .25)

## plot lat and lng points onto state map
with(rt_dmbbll, points(lng, lat, pch = 20, cex = .75, col = rgb(0, .3, .7, .75)))
```

#### `stream_tweets`

<https://developer.twitter.com/en/docs/tweets/search/api-reference/get-search-tweets>

- `q`
  - Sampling a small random sample of all publicly available tweets `q=""`
  - Filtering via a search-like query (up to 400 keywords) `q="duke,basketball"`. "," separation
  - Tracking via vector of user ids (up to 5000 user_ids) `q="hillaryclinton,realdonaldtrump"`. "," separation
  - Location via geo coordinates (1-360 degree location boxes) `q=c(-125, 26, -65, 49)`
- `timeout` : amount of time (seconds) **occupy your r session**
- `parse`: TRUE(dataframe); FALSE(JSON).
- `file_name`: save as a file

**Usually the file is large. Recommend to save as JSON file then parse to data.frame.**

To ensure the stream automatically reconnects following any interruption prior to the specified stream time, use `stream_tweets2()`.

```{r,echo=TRUE,cache=TRUE}
## Randomly sample (approximately 1%) from the live stream of all tweets for 30 seconds (default)
rt <- stream_tweets("")
nrow(rt)

rt <- stream_tweets("duke,bluedevil,unc")
nrow(rt)
rt
## stream tweets for a day (60 secs x 60 mins * 24 hours )
stream_tweets(
  "abc,nbcnews,cbsnews,nytimes,bbcworld,bbcbreaking,bbcnews,bbcsport",
  timeout = 60*2,
  file_name = "tweetsth1.json",
  parse = FALSE
)

## read in the data as a tidy tbl data frame
djt1 <- parse_stream("tweetsth1.json")
djt1
```

#### Other functions

<https://rtweet.info/reference/index.html>


### Retweet networks

Retweet networks: create networks based on datasets

directed: retweet

Similarly, we can get quote networks, replying networks.

```{r,echo=TRUE,cache=TRUE}
rt_duke <- search_tweets(
  "#duke", n = 1000
)
nrow(rt_duke)
names(rt_duke)

netdf=rt_duke%>%dplyr::select(.,screen_name,retweet_screen_name,is_retweet)
netdfr=netdf%>%filter(is_retweet)%>%select(-is_retweet)
netdfp=netdf%>%filter(!is_retweet)%>%pull(screen_name)
igra_duke=graph_from_data_frame(netdfr)#+netdfp
E(igra_duke)$weight=rep(1,ecount(igra_duke))
igra_duke_s <- igraph::simplify( igra_duke, remove.multiple = T, remove.loops = F, 
                 edge.attr.comb=c(weight="sum"))
igra_duke_s
plot(igra_duke_s,vertex.color="gold", vertex.size=log(igraph::degree(igra_duke_s))*3+1, 
     vertex.frame.color="gray", vertex.label.color="black", 
     vertex.label.cex=log(igraph::degree(igra_duke_s))*0.2+0.1, vertex.label.dist=2, edge.curved=0.5,edge.arrow.size=.2)
```


### Friendship networks

#### `get_friends()`

Friendship network of NYC political science

directed: following

`get_friends()`: Get user IDs of accounts followed by target user(s).

```{r,echo=TRUE,cache=TRUE}
##maximum ids: 100
user.seed="drewconway"
user.following=get_friends(user.seed,n=500,retryonratelimit = TRUE)
nrow(user.following)
user.following%>%head(5)

```

#### filter on the following user list

```{r,echo=TRUE,cache=TRUE}
info.following=lookup_users(user.following$user_id)
info.following
names(info.following)
##choose the filtering criterion: description, verified (blue check mark), location
info.following%>%select(geo_coords,country,country_code,location)%>%lat_lng()
## filter based on description
candidates=info.following%>%filter(description%>%
                          str_detect("nyu|new york university"),
                        description%>%
                          str_detect("poli(tics|tical|sci|cy)"))%>%
  select(user_id,screen_name,name,friends_count,description)
candidates%>%head(5)
```

#### request rate limit

`rate_limit`

<https://developer.twitter.com/en/docs/developer-utilities/rate-limit-status/api-reference/get-application-rate_limit_status>


```{r,echo=TRUE,cache=TRUE}
rate_limit()%>%head()
rate_limit("get_friends")
get_friends(c("drewconway","BarackObama"))
rate_limit("get_friends") # 15 every 15 min
rate_limit("lookup_users") # 900 every 15 min
```


```{r,echo=TRUE,cache=TRUE,eval=FALSE}
limit.fri=rate_limit("get_friends")
  if (limit.fri$remaining==0){
    Sys.sleep(60*as.numeric(limit.fri$reset))}
```

#### Friendship network 

```{r,echo=TRUE,cache=TRUE,eval=FALSE}
# seed user
user.seed= 20916144 #"cdsamii"
user.following=get_friends(user.seed,n=15,retryonratelimit = TRUE)
userid=c(user.seed,user.following$user_id)
info.following=lookup_users(userid)
user.df=info.following%>%filter(description%>%
                          str_detect(regex("nyu|new york university",ignore_case = T)),
                        description%>%
                          str_detect(regex("poli(tics|tical|sci|cy)",ignore_case = T))
                        )%>%
  select(user_id,screen_name,name,friends_count,description)
acc.id=user.df$user_id # qualified id
nyc.id=user.seed # already scrapped the friends
can.id=acc.id[!acc.id%in%nyc.id] # to be scrapped
rej.id=userid[!info.following$user_id%in%acc.id] # non-qualified
edge.list=user.following%>%filter(user_id%in%acc.id) # netowork
info.id=userid # already request user info
while((length(nyc.id)<100)){
  # pick the first user in the acc.id
user.following=get_friends(can.id,n=1000,retryonratelimit = TRUE)
userid=user.following$user_id
useridx=userid[!userid%in%info.id] # new userid
info.following=lookup_users(useridx)
user.dfx=info.following%>%filter(description%>%
                          str_detect(regex("nyu|new york university",ignore_case = T)),
                        description%>%
                          str_detect(regex("poli(tics|tical|sci|cy)",ignore_case = T))
                        )%>%
  select(user_id,screen_name,name,friends_count,description)
nyc.id=c(nyc.id,can.id)%>%unique() #already scrapped and in the list
if(nrow(user.dfx)==0){break}
user.df=rbind(user.df,user.dfx) #merge user info df
can.id=user.dfx$user_id #to be scrapped
rej.idx=useridx[!useridx%in%can.id] #not qualified
rej.id=c(rej.id,rej.idx)%>%unique()
acc.id=c(acc.id,can.id)%>%unique()
info.id=c(info.id,useridx)%>%unique()
edge.listx=user.following%>%filter(user_id%in%acc.id) #add edgelist
edge.list=rbind(edge.list,edge.listx)
}
```

#### Network Visualization

```{r,echo=TRUE,cache=TRUE}
load("images/friendship.rdata")
edge.list%>%head(5)
user.df%>%head(5)
library(igraph)
net=graph_from_data_frame(edge.list)
netsim=igraph::simplify(net, remove.multiple = T, remove.loops = F)
V(netsim)$id=V(netsim)$name

user.df=user.df %>%
  unique()%>%
    arrange(match(user_id, V(netsim)$id))
user.name=user.df%>%
  pull(name)
V(netsim)$name=user.name
V(netsim)$degree=user.df$friends_count
set.seed(123)
plot(netsim,vertex.name=V(netsim)$user.name,vertex.color="gold", vertex.size=log(V(netsim)$degree)*.8+0.01, 
     vertex.frame.color="gray", vertex.label.color="black", 
     vertex.label.cex=0.5, vertex.label.dist=2, edge.curved=0.5,edge.arrow.size=.2,vertex.label.cex=.5,vertex.label=NA)
```


## Other APIs

- [`Rfacebook`])(https://cran.r-project.org/web/packages/Rfacebook/Rfacebook.pdf) (facebook) 
- [`RedditExtractoR`](https://cran.r-project.org/web/packages/RedditExtractoR/RedditExtractoR.pdf) (reddit) 

- [`imdbapi`](https://cran.r-project.org/web/packages/imdbapi/imdbapi.pdf) (IMDB)

- [`omdbapi`](https://github.com/hrbrmstr/omdbapi)(The Open Movie Database)


## API request directly from R

### Introduction

The movie database API <https://www.themoviedb.org/>

- Signup and request for an API key <https://developers.themoviedb.org/3/getting-started/introduction>
- Write functions to make query:
  - Create a query
  - From JSON file to dataframe
- Build your own network based on these functions

### preparation

```{r, echo=TRUE, message=FALSE, warning=FALSE}
#install.packages("rjson")
library(rjson)
#install.packages("jsonlite")
library(jsonlite)
```

### search people id

Search people based on the name:
<https://developers.themoviedb.org/3/search/search-people>

```{r,echo=TRUE,eval=FALSE}
### get actor/director id based on name
get_search_people = function(people,api="YOUR_API_ACCOUNT"){
  
  search = URLencode(people, reserved = TRUE) 
  
  people_url = paste0("https://api.themoviedb.org/3/search/person?api_key=",api,"&language=en-US&query=",
                      search,"&include_adult=false")
  people_json = jsonlite::fromJSON(paste(readLines(people_url), collapse=""))
  
  total_page = people_json$total_pages
  if (total_page > 1){
    people_id_df = data.frame()
    n = min(5, total_page)
    for (j in 1:n){
      url = paste0("https://api.themoviedb.org/3/search/person?api_key=",api,"&language=en-US&query=",
                   search,"&page=",j,"&include_adult=false")
      json = jsonlite::fromJSON(paste(readLines(people_url), collapse=""))
      temp = json$results %>% as.data.frame() %>% select(id, name)
      people_id_df = rbind(people_id_df, temp)
    }
  } else {
    people_id_df = people_json$results %>% as.data.frame() %>% select(id, name)
  }
  
  return(people_id_df) # this dataframe only contains name and people id
  
}
actress="Julianne Moore" # She comes from NC
get_search_people(actress)
people=actress
```

### search movies based on people id

Search the movies of one person based on id:<https://developers.themoviedb.org/3/people/get-person-movie-credits>


```{r,echo=TRUE,eval=FALSE}
# get movie details of one person with the person id
get_people_movie = function(id,api="YOUR_API_ACCOUNT"){
  
  url = paste0("https://api.themoviedb.org/3/person/",id,"/movie_credits?api_key=",api,"&language=en-US")
  people_movie_json = jsonlite::fromJSON(paste(readLines(url), collapse=""))
  people_movie_df = people_movie_json$cast %>% as.data.frame() %>% select(character, poster_path, id, vote_average, original_language,
                                                                          title, popularity, overview, release_date)
  base_url = "http://image.tmdb.org/t/p/w500" 
  people_movie_df = people_movie_df %>% mutate(poster_path = paste0(base_url, poster_path))
  
  return(people_movie_df)
  
}
id=1231 # got from the previous function `get_search_people`
get_people_movie(id)

```




